Structured Versus Decorated Cospans

### 2020-11-26 cospans.tex
wrorked on Section 5.1 - lax monoidal pseudofunctor

We can make $F$ into a symmetric lax monoidal pseudofunctor $F \maps (\Fin\Set, +) \to (\Cat,\times)$ by equipping it with suitable functors 
\[   \phi_{N,N'} \maps F(N) \times F(N') \to F(N+N'), \qquad \phi_0 \maps F(\emptyset) \to 1 \in \Cat. \]  
The functor $\phi_0$ is uniquely determined since $1$ is the terminal category.   More interesting is $\phi_{N,N'}$.   This functor maps a pair of graph structures $s, t \maps E \to N$ and $s',t' \maps E' \to N'$ to the graph structure $s+s', t+t' \maps E+E' \to N+N'$.  In other words, it sends a pair of graph structures to their `disjoint union'.   Even though $F \maps \Fin\Set \to \Cat$ is a functor (e.g., composition is strictly preserved), this choice of $\phi_0$ and $\phi_{N,N'}$ does not make $F$ into a symmetric lax monoidal functor, since the required laws hold only up to a natural isomorphism.   See \cite[Section 5]{BC} for a proof that these laws fail to hold `on the nose'.   This fact necessitates a generalization of Fong's original formalism.

>>>>

We can make $F$ into a symmetric lax monoidal pseudofunctor $F \maps (\Fin\Set, +) \to (\Cat,\times)$ by equipping it with suitable functors 
\[   \phi_{N,N'} \maps F(N) \times F(N') \to F(N+N'), \qquad \phi_0 \maps F(\emptyset) \to 1 \in \Cat. \]  
The functor $\phi_0$ is uniquely determined since $1$ is the terminal category.   More interesting is $\phi_{N,N'}$.   This functor maps a pair of graph structures $s, t \maps E \to N$ and $s',t' \maps E' \to N'$ to the graph structure $s+s', t+t' \maps E+E' \to N+N'$.  In other words, it sends a pair of graph structures to their `disjoint union'.   Surprisngly, though $F \maps \Fin\Set \to \Cat$ is a functor---for example, composition is strictly preserved---this choice of $\phi_{N,N'}$ does not make $F$ into a symmetric lax monoidal functor, since the required laws hold only up to natural isomorphism.   See \cite[Section 5]{BC} for a proof that these laws fail to hold on the nose.   This fact necessitates a generalization of Fong's original formalism.
